From Freebase to Wikidata: The Great Migration

### 2015-10-14 paper.tex
Fix typo.
Add architecture diagram.

Entities and statements are stored in an SQL database (MySQL or SQLite) and
follow the Wikidata data structure with an additional status field to keep track
of statements that have already been approved or rejected, or not yet
visited. Statements can be grouped in ``datasets'' and ``uploads'' to
distinguish data from different sources.\footnote{At the time of this writing,
  the backend contained 5 different datasets}

The REST API of the backend supports the following types of queries:
\begin{itemize}
\item Get an entity (i.e. its statements) by Wikidata QID
  (e.g. \verb|GET /entities/Q2529789|).
\item Get a random entity with unapproved (or approved, rejected) statements
  (\verb|/entities/any|).
\item Get a statement by database ID (\verb|GET /statements/1|) or get a list of
  random statements (\verb|GET /statements/any|).
\item Set a new state for a statement \\(\verb|POST /statements/1?state=approved&user=Alice|).
\end{itemize}
All GET requests support an additional \Verb|state=...| query parameter to
filter by state. This allows Wikidata developers to analyse statements that have
already been updated (e.g. ``return 10 random rejected statements'') for further
analysis. The default of this parameter is \verb|unapproved|.

@@

\todo{Review and expand}

>>>>

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\columnwidth]{img/architecture.png}
    \caption{Sources Tool Architecture. The frontend is implemented in
      Javascript and sends REST requests to the C++ backend to retrieve and
      update entities or statements, which are stored in a relational database.}
    \label{fig:architecture}
\end{figure}

Entities and statements are stored in a relational database (MySQL or SQLite) and
follow the Wikidata data structure with an additional status field to keep track
of statements that have already been approved or rejected, or not yet
visited. Statements can be grouped in ``datasets'' and ``uploads'' to
distinguish data from different sources.\footnote{At the time of this writing,
  the backend contained 5 different datasets}

The REST API of the backend supports the following main types of requests:
\begin{itemize}
\item Get an entity (i.e. its statements) by Wikidata QID
  (e.g. \verb|GET /entities/Q2529789|).
\item Get a random entity with unapproved (or approved, rejected) statements
  (\verb|/entities/any|).
\item Get a statement by database ID (\verb|GET /statements/1|) or get a list of
  random statements (\verb|GET /statements/any|).
\item Set a new state for a statement \\(\verb|POST /statements/1?state=approved&user=Alice|).
\end{itemize}
All GET requests support an additional \verb|state=...| query parameter to
filter by state. This allows Wikidata developers to analyse statements that have
already been updated (e.g. ``return 10 random rejected statements'') for further
analysis. The default of this parameter is \verb|unapproved|.

@@
